Equations & R Code

### 2017-02-23 manuscript/coexistence-stability_ms.Rmd
adds 8 species storage effect model and results; some minor text additions to ms

>>>>

\new{To bound the problem and to isolate the effect of fluctation-dependent coexistence on the diversity-ecosystem stability relationship we constrain our analysis to four species communities and do not consider communities where coexistence is maintained by a combination of mechanisms.
We limit our analysis to four species communities to keep the models tractable while still allowing enough of a species richness gradient for trends to emerge.
It is notoriously difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning (Yuan \& Chesson 2015), which would then cloud our inference on the effect of fluctuation-dependent coexistence.
It is relatively easy to get many species to coexist via the storage effect, but for consistency we constrain our focus to four species communities under the storage effect as well.}
